Run AwAI: StarCraftII Adversary Avoidance Using Neural Networks and Genetic Algorithms

### 2018-06-02 paper.tex
more papering

We chose to use our neural network to represent a function taking an input
vector consisting of relative agent position and adversary's relative position
and return an output vector of directions.
\begin{align}
  \bm{V} = \mathcal{N}(\bm{I})
\end{align}
We choose the next action according to the equation:
\begin{align}
  a_n = \max_{v \in \bm{V}} v
\end{align}
This input vector is flexible, and allows us to tweak the information that we
feed to the neural network. Additionally, while the output space we used
contains only movement in the cardinal directions, we could easily add other
supported actions like attacking and mining resources.

@@

\section{Results}

\section{Conclusion}
Different selection types?
\subsection{Improvements}
\subsection{Future Work}

>>>>

We chose to use our neural network to represent a function taking an input
vector consisting of relative agent position and adversary's relative position
and return an output vector of directions.
\begin{align}
  \bm{V} = \mathcal{N}(\bm{I})
\end{align}
Where $\mathcal{N}$ is the function computed by our neural network. We choose
the next action according to the equation:
\begin{align}
  a_n = \max_{v \in \bm{V}} \: v
\end{align}
This input vector is flexible, and allows us to tweak the information that we
feed to the neural network. Additionally, while the output space we used
contains only movement in the cardinal directions, we could easily add other
supported actions like attacking and mining resources.

@@

\section{Results}
%% TODO: Talk about choice of hyper paramters, population size, episode count
%% mutation constants, eta in fitness function

\section{Conclusion}
Different selection types?

\subsection{Improvements}

\subsection{Future Work}
This project can certainly be extended in many ways, for example, we could
extend the output vectors to include offinsive manuvering by our agent, and
train the agent to be agressive by considering the numebr of adversaries killed
by our agent during the simulation.
